Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
general editing

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms that can appear in queries.
\item SSQ ontologies, used to describe the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. The realm of automobiles (which
we use for illustration in this paper) contains, for example,
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia \cite{Auer07dbpedia:a}.
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to Wikipedia documents which provides us with a large
realm-specific document corpus.

@@

To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass/subclass} relationships built using DBPedia properties \textit{broader/narrower}. By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.

@@

Once the semantic hierarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
contains a set of information pages, P, that correspond to concepts
that share said category. Considering that the categorical structure
is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
a particular category. The category's that The assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.

The subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing …) can be seen as grabbing
information specific to the category. The super categories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motor Sport, Individual Sport...) are an abstract description of
the subcategories.

>>>>

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms appearing in queries.
\item SSQ ontologies, describing the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. For example, the realm of automobiles (which
we use for illustration in this paper) contains 
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia \cite{Auer07dbpedia:a}.
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to Wikipedia documents which provides us with a large
realm-specific document corpus.

@@

To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}. By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.

@@

Once the semantic hierarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/Wikipedia heterarchy
contains a set of information pages, P, corresponding to the concepts shared by the category. Since the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket \cite{Friedman97bayesiannetwork} to describe
a particular category. Our assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.

The subcategories of the category Automobiles (Driving, Traffic Law,
Automobiles by Decade, and Auto Racing) can be seen as grabbing
information specific to the category. The super categories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motor Sport, Individual Sport...) are an abstract description of
the subcategories.
